Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-07-29 MSc-dissertation.tex
New para

@@

>>>>

When we are trying more populations, an `over-fitting' behaviour is observed at the trajectory of macrophage (FIGURE). In this case, the discrepancy of simulated data and observed data comes from the last 2 data point (72 hpl and 120 hpl).

Next, we performed a model selection on model 3, 4 and 5. FIGURE shows the model probabilities at different generations. From population 10 to population 20 model 4 gains advantage but after population 20 model 5 is preferred. Again, as DISCUSSED in the model comparison of model 1, 2 and 3, we considered the the violently changing model probability is related to the inference ability at certain epsilon threshold values (epsilon) and possibly the insufficient exploration of the parameter space. Given the present result, model 5 is regarded as the best model. Some further experiments tried larger population size (10,000 particles per population) and more populations (36 populations), but the resultant model did not have a significantly better fit of the observed data, although much more computation resources are used.

A inferred parameter posterior distribution of model 5 is shown in FIGURE. SOME DESCRIPTION.

\subsection{Sensitivity of parameters}

[why last PCs]

[which parameters are most sensitive]

[what does that mean]

@@

[possible reasons]
